---
title: "Econometriscs assignment"
author: "Heidi Marie Rolfsnes and Ann Elisabeth Jacobsen"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r Packages}
#| echo = FALSE
suppressMessages(library(tidyverse))
suppressMessages(library(lubridate))
suppressMessages(library(tibble))
suppressMessages(library(readr))
suppressMessages(library(knitr))
suppressMessages(library(dplyr))
suppressMessages(library(dineq))
suppressMessages(library(magrittr))
options(scipen = 999)

```
# MSB104 Econometrics
This is a collection of assignments in the subject econometrics MSB104.

#Assignment 1
In this assignment we are looking at five European countries: Denmark, France, Hungary, Portugal and Slovakia. 
In the first assignment we have collected data from Eurostats, the data contains GDP and populations for the countries but also at NUTS3 level for the last 20 years. 

We collected 2 datasets, and the first thing we did was to clean the list and remove data that didn’t have any valuables. We changed the names on some of the variables and merged the two datasets into one dataset called BNP2.


```{r GDP from Denmark, France, Hungary, Portugal and Slovakia}
#| echo = FALSE
BNP<- read.csv("nama_10r_3gdp.csv")
BNP <- BNP %>% 
  select(unit, geo, TIME_PERIOD, OBS_VALUE) %>%
      rename(GDP = "OBS_VALUE",Year = "TIME_PERIOD", Regio_id = "geo") 

#In this dataset we can see the GDP from Denmark, France, Hungary, Portugal and Slovakia
```

```{r  Population from Denmark, France, Hungary, Portugal and Slovakia}
#| echo = FALSE
Pop<- read_csv("demo_r_pjanaggr3.csv", show_col_types = FALSE)
Pop <- Pop %>% 
  select(geo, TIME_PERIOD, OBS_VALUE) %>%
      rename(Population = "OBS_VALUE",Year_pop = "TIME_PERIOD") 
#In this dataset we can see the population from Denmark, France, Hungary, Portugal and Slovakia
  
```

```{r GDP and Population - together}
#| echo = FALSE
 BNP2<- BNP %>%
      select(unit, Regio_id,Year, GDP) %>%
      left_join(Pop, by = c("Year" = "Year_pop", "Regio_id" = "geo"))
# We took the GDP- and the populationdataset  together in one data, called BNP2
```


Then we calculated the GDP pr capita. We did that by divide the GDP and the population. To get the right number we multiplied with a million.

```{r Calculate GDP per capita}
#| echo = FALSE
BNP2 <- BNP2 %>%
mutate(Per_capita =   GDP/Population*1000000) %>%
na.omit()
#NA variables are removed
```

We have divided the countries into NUTS3 levels. To get the result by country, we made a summary of GDP per capita on every country. By creating such a summary for each country, we can get an overview of whether there are major inequality within the various regions. If we find such deviations, we can choose to remove some of our regions in order not to have large inequalities. 


##Denmark

Denmark are missing observations for some of the years, so there are less data to be collected about them. Denmark is also a small country so there are not that many NUTS2 regions.  

```{r Denmark}
#| echo = FALSE
DK <- group_by(BNP2, Regio_id, Year) %>%
filter(Regio_id %in% c("DK011", "DK012", "DK013", "DK014", "DK021", "DK022", "DK031", "DK032", "DK041", "DK042", "DK050", "DKZZZ")) %>%
	 select("Year", "Regio_id", "Per_capita", "Population")
```

**Country level**

```{r Mean: GDP Per Capita in Denamrk}
	summarise(DK, GDP_per_Capita = mean(Per_capita))
```


```{r}
summary(DK)
```

##France

France is a large country, it has over a hundred NUTS3 regions. 

```{r France}
#| echo = FALSE
FR <- group_by(BNP2, Regio_id, Year) %>%
filter(Regio_id %in% c("FR101", "FR102", "FR103", "FR104", "FR105", "FR106", "FR107", "FR108", "FRB01", "FRB02", "FRB03", "FRB04", "FRB05", "FRB06" , "FRC11", "FRC12","FRC13", "FRC14", "FRC21", "FRC22, FRC23", "FRC24", "FRD11", "FRD12","FRD13", "FRD21", "FRD22, FRE11", "FRE12", "FRE21", "FRE22", "FRE23","FRF11", "FRF12", "FRF21", "FRF22, FRF23", "FRF24", "FRF31", "FRF32", "FRF33","FRF34", "FRG01", "FRG02", "FRG03, FRG04", "FRG05", "FRH01", "FRH02", "FRF03, FRH04", "FRI11", "FRI12", "FRI13", "FRI14, FRI15", "FRI21", "FRI22", "FRI23, FRI31", "FRI32", "FRI33", "FRI34","FRJ11", "FRJ12",	"FRJ13",	"FRJ14",	"FRJ15",	"FRJ21",	"FRJ22",	"FRJ23",	"FRJ24",	"FRJ25",	"FRJ26",	"FRJ27"	,"FRJ28",	"FRK11",	"FRK12",	"FRK13",	"FRK14",	"FRK21",	"FRK22",	"FRK23",	"FRK24",	"FRK25",	"FRK26",	"FRK27",	"FRK28",	"FRL01",	"FRL02",	"FRL03",	"FRL04",	"FRL05",	"FRL06",	"FRM01",	"FRM02","FRXXX",	"FRY10",	"FRY20",	"FRY30",	"FRY40",	"FRY50")) %>%
 select("Year", "Regio_id", "Per_capita", "Population")
```

```{r}
summary(FR)
```

In the summary of France there are a hug differense in min and max. this is because France has colonies in other countries that are counted, these colonies are located in Africa and South America which have a negative effect on the overall GDP of France. 'further research then these countries should be removed from the data set.


```{r France without the FRY regions}
#| echo = FALSE
FR1 <- group_by(BNP2, Regio_id, Year) %>%
filter(Regio_id %in% c("FR101", "FR102", "FR103", "FR104", "FR105", "FR106", "FR107", "FR108", "FRB01", "FRB02", "FRB03", "FRB04", "FRB05", "FRB06" , "FRC11", "FRC12","FRC13", "FRC14", "FRC21", "FRC22, FRC23", "FRC24", "FRD11", "FRD12","FRD13", "FRD21", "FRD22, FRE11", "FRE12", "FRE21", "FRE22", "FRE23","FRF11", "FRF12", "FRF21", "FRF22, FRF23", "FRF24", "FRF31", "FRF32", "FRF33","FRF34", "FRG01", "FRG02", "FRG03, FRG04", "FRG05", "FRH01", "FRH02", "FRF03, FRH04", "FRI11", "FRI12", "FRI13", "FRI14, FRI15", "FRI21", "FRI22", "FRI23, FRI31", "FRI32", "FRI33", "FRI34","FRJ11", "FRJ12",	"FRJ13",	"FRJ14",	"FRJ15",	"FRJ21",	"FRJ22",	"FRJ23",	"FRJ24",	"FRJ25",	"FRJ26",	"FRJ27"	,"FRJ28",	"FRK11",	"FRK12",	"FRK13",	"FRK14",	"FRK21",	"FRK22",	"FRK23",	"FRK24",	"FRK25",	"FRK26",	"FRK27",	"FRK28",	"FRL01",	"FRL02",	"FRL03",	"FRL04",	"FRL05",	"FRL06",	"FRM01",	"FRM02","FRXXX")) %>%
 select("Year", "Regio_id", "Per_capita", "Population")
````

**Country level**
```{r Mean: GDP Per Capita in France}
	summarise(FR, GDP_per_Capita = mean(Per_capita))
```

```{r}
summary(FR1)
```	
##Hungary

```{r Hungary}
#| echo = FALSE
HU <- group_by(BNP2, Regio_id, Year) %>%
filter(Regio_id %in% c("HU110", "HU120","HU211","HU212", "HU213", "HU221", "HU222","HU223","HU231", "HU232", "HU233", "HU311", "HU312", "HU313", "HU321", "HU322", "HU323", "HU331", "HU332", "HU333", "HUXXX")) %>%
 select("Year", "Regio_id", "Per_capita", "Population")
	
```

**Country level**

```{r Mean: GDP Per Capita in Hungary}
	summarise(HU, GDP_per_Capita = mean(Per_capita))
```

```{r}
summary(HU)
```

## Portugal

```{r Portugal}
#| echo = FALSE
#Gen data Portugal
PT <- BNP2 %>%
filter(Regio_id %in% c("PT111","PT112","PT119","PT11A","PT11B","PT11C", "PT11D","PT11E",	"PT16B",	"PT16D",	"PT16E",	"PT16F",	"PT16G",	"PT16H",	"PT16I",	"PT16J",	"PT170",	"PT181",	"PT184",	"PT185",	"PT186",	"PT187",	"PT200",	"PT300")) %>%
 select("Year", "Regio_id", "Per_capita", "Population") 

```
**Country level**
```{r Mean: GDP Per Capita in Portugal}
	summarise(PT, GDP_per_Capita = mean(Per_capita))
```
**Regional level (NUTS3)**


##Slovakia

```{r Slovakia}
#| echo = FALSE
SK <- group_by(BNP2, Regio_id, Year) %>%
filter(Regio_id %in% c("SK010", "SK021","SK022","SK023", "SK031", "SK032", "SK041", "SK042")) %>%
 select("Year", "Regio_id", "Per_capita", "Population")

```
**Country level**
```{r Mean: GDP Per Capita in Slovakia}
	summarise(SK, GDP_per_Capita = mean(Per_capita))
```

```{r}
summary(SK)
```



### Descriptive Statistics regional inequity (Gini Nuts2) 

We are trying to get the Nuts2 regions, but we only get the nuts 3. 

```{r Denmark gini}
#| echo = FALSE
#Nuts 2 id
DK %>%  
  mutate(id_nuts2 = substr(Regio_id,1,4)) 
#Nuts 1 id
DK %>%  
  mutate(id_nuts0 = substr(Regio_id,1,2))

#gen weighted gini
#for all
gini.wtd(DK$Per_capita, w = DK$Population)


DK %>% 
  mutate(gini_n2 = gini.wtd(Per_capita, w = Population)) %>%
  ungroup() # to remove grouping

summary(DK$gini_n2 )

```
```{r France gini}
#| echo = FALSE
#Nuts 2 id
FR1 %>%  
  mutate(id_nuts2 = substr(Regio_id,1,4)) 
#Nuts 1 id
FR1 %>%  
  mutate(id_nuts0 = substr(Regio_id,1,2))

#gen weighted gini
#for all
gini.wtd(FR1$Per_capita, w = FR1$Population)


FR1 %>% 
  mutate(gini_n2 = gini.wtd(Per_capita, w = Population)) %>%
  ungroup() # to remove grouping

summary(FR1$gini_n2 )

```

```{r Hungary gini}
#| echo = FALSE
#Nuts 2 id
HU %>%  
  mutate(id_nuts2 = substr(Regio_id,1,4)) 
#Nuts 1 id
HU %>%  
  mutate(id_nuts0 = substr(Regio_id,1,2))

#gen weighted gini
#for all
gini.wtd(HU$Per_capita, w = HU$Population)


HU %>% 
  mutate(gini_n2 = gini.wtd(Per_capita, w = Population)) %>%
  ungroup() # to remove grouping

summary(HU$gini_n2 )

```

PT2 <-PT %>%  
  select(Regio_id) 
filter (temp_var == 4) %>%


```{r Portugal gini}
#| echo = FALSE
#Nuts 2 id
PT %>%  
  mutate(id_nuts2 = substr(Regio_id,1,4)) 
#Nuts 1 id
PT %>%  
  mutate(id_nuts0 = substr(Regio_id,1,2))

#gen weighted gini
#for all
gini.wtd(PT$Per_capita, w = PT$Population)


PT %>% 
  mutate(gini_n2 = gini.wtd(Per_capita, w = Population)) %>%
  ungroup() # to remove grouping

summary(PT$gini_n2 )

```

```{r Slovakia gini}

SK %>%
  mutate(id_nuts2 = substr(Regio_id,1,4))

SK %>%
  mutate(id_nuts0 = substr(Regio_id,1,2))

gini.wtd(SK$Per_capita, w = SK$Population)

SK %>%
  mutate(gini_n2 = gini.wtd(Per_capita, w = Population)) %>%
ungroup()

summary(SK$gini_n2)

```


