---
title: "Econometriscs assignment"
author: "Heidi Marie Rolfsnes and Ann Elisabeth Jacobsen"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r Packages}
#| echo = FALSE
suppressMessages(library(tidyverse))
suppressMessages(library(lubridate))
suppressMessages(library(tibble))
suppressMessages(library(readr))
suppressMessages(library(knitr))
suppressMessages(library(dplyr))
suppressMessages(library(dineq))
suppressMessages(library(magrittr))
suppressMessages(library(vtable))
suppressMessages(library(wooldridge))
options(scipen = 999)

```
## Introduction   
In the subject MSB104 econometrics, this year we will hand in an assignment divided into four assignments throughout the semester. The assignments must be written and calculated in the software R. We are group one and the countries that will be representing in our assignment is: Denmark, France, Hungary, Portugal and Slovakia.

## Assignment 1

In this assignment we are going to download two dataset from Eurostat. The data contains GDP (nama_10r_3gdp) and populations (demo_r_pjanaggr3,pi) for countries over the last 20 years, on a NUTS3 level. 
When we have all the information we need from the dataset, we are going to calculate the GDP per capita and describe the data by using the meta data description from Eurostat. 

In the second part of this assignment we will use our data to calculate the population watertight GDP Ginie coefficients for the European NUTS2 (j) level and describe our new data. Then we are going to plot the distribution of Ginie coefficients
In the end of the first assignment we will discuss if there are noteworthy outliers.


### Dataset
The original dataset "Nama_10r_3gdp" contains GDP for many countries. We have only downloaded information on our five countries on a NUTS3 level. The datset is structured in eight columns and each column present different data values. We are looking for the GDP values and it emerges from the column "OBS_VALUE". The column "GEO" tells us which geographical region the value belongs to.
There is also a column for year named "TIME_PERIOD". We are going to work with these three columns and will start with rename the names of the columns. 
There are different types of GDP values and the unit is stored in a column named "UNIT", we have chosen to use values where unit is MIO_EUR. This unit represents the GDP value in million Euros.


```{r Dataset GDP and rename obs_value, time_period and geo}
#| echo = FALSE
BNP<- read.csv("nama_10r_3gdp.csv")
BNP <- BNP %>% 
  select(unit, geo, TIME_PERIOD, OBS_VALUE) %>%
      rename(GDP = "OBS_VALUE",Year = "TIME_PERIOD", Regio_id = "geo") 

#In this dataset we can see the GDP from Denmark, France, Hungary, Portugal and Slovakia
```

The dataset Demo_r_pjanaggr3 contains population data on nuts3 level for our five countries.
The two datasets we obtained from Eurostat are quite similar and the population dataset also contains Time_period, Obs_value and geo. We will rename the names of the columns we will use, in the same way as we did in the GDP dataset.

```{r  Dataset Population and rename obs_value and time_period}
#| echo = FALSE
Pop<- read_csv("demo_r_pjanaggr3.csv", show_col_types = FALSE)
Pop <- Pop %>% 
  select(geo, TIME_PERIOD, OBS_VALUE) %>%
      rename(Population = "OBS_VALUE",Year_pop = "TIME_PERIOD") 
#In this dataset we can see the population from Denmark, France, Hungary, Portugal and Slovakia
  
```

We made a new dataset called BNP2 (Norwegian word for GDP and a number). In this dataset we will gather the information we need from the other two datasets and combine them into one dataset. This will do it easier in our ongoing research.  

```{r Make one datset with GDP and Population}
#| echo = FALSE
 BNP2<- BNP %>%
      select(unit, Regio_id,Year, GDP) %>%
   filter(unit =='MIO_EUR' & (grepl('DK...', Regio_id) | grepl('FR...', Regio_id) | grepl('HU...', Regio_id) | grepl('PT...', Regio_id)| grepl('SK...', Regio_id))) %>%
  left_join(Pop, by = c("Year" = "Year_pop", "Regio_id" = "geo"))
```

```{r}
#| echo = FALSE
BNP2 %>%
  vtable::st(.)
```


## GDP per Capita 

To calculate GDP per capita, we have taken GDP and divided it by the population. And then we have multiplied by one million, so that it is represented correctly in Euros, also like it is in the unit.

```{r Calculate GDP per capita}
#| echo = FALSE
BNP2 <- BNP2 %>%
mutate(Per_capita =   GDP/Population*1000000) %>%
na.omit()
#NA variables are removed
```


Briefly about what we found in the summary. We found the min and the max values. i.e. the smallest and the highest GDP per capita for the country. We also found 1st quartile and 3rd quartile. The first quartile was the observation between the median and the lowest value, and looks at the 25% lowest values from the 75% highest. The median looks at the value that is observed the most times in the middle of the observations. The third quartile is then, naturally enough, the value between the median and the highest value.We have also look at mean which told us what the average observation for all regions was.

And then we further look at GDP, population and GDP per capita in our five countries and what results it gaves us when we calculate all the NUTS3 regions together.
```{r}
#| echo = FALSE
GDP2 <- BNP2 %>%
filter(unit == "MIO_EUR" & (grepl('DK..', Regio_id) | grepl('FR..', Regio_id) | grepl('HU..', Regio_id)| grepl('PT..', Regio_id) | grepl('SK..', Regio_id))) 
```

```{r Mean: GDP Per Capita in all countries}
	summarise(GDP2, GDP_per_Capita = mean(Per_capita))
```
From the summary we can see that GDP per capita at NUTS3 level for all our countries was 22 805,13 Euro. since we don't have any other values to compare with we can't say if this is good or bad. 

```{r}
summary(GDP2)
```

It wasn't easy to draw any conclusion from this summary above. We can see that there is a very big difference in GDP as the lowest value is 750,8 while the highest is 251 623,3. We can also see that the maximum value is high compared to the other values, as the 3rd quartile is only 18 630. Population and Per_capita gave us the same results, with a very low minimum and a high maximum value. 


```{r NUTS3}
  ggplot(GDP2, aes(x = Year, y= Per_capita, fill= Regio_id, color= Regio_id)) +
  geom_point(lwd = .8) +
   labs(x = "Year", y = "Per_capita") 
```

This ggplot shows GDP pr capita for all our countries. over the last 20 years. 
it shows that ....


To get a better picture of the different countries and the opportunity to see if there are regions that stand out. We make summaries per country, because then we had the opportunity to exclude regions that stand out in futher assignments. We will also look at a spesific year for all the country to compare results with.

To get the result by country, we made a summary of GDP per capita on each country. By creating such a summary for each country, we can get an overview of whether there are major inequality within the various regions. If we find such deviations, we can choose to remove some of our regions in order not to have large inequalities.

We startet with Denmark and then we took the countries alphabetically.

###Denmark

Denmark is a small country in Scandinavia,and they don't have many NUTS2 regions.   Denmark consists of many islands, on which the regions are divided. Kobenhagen is the capital of Denmark 

```{r Denmark}
#| echo = FALSE
DK <- BNP2 %>%
filter(Regio_id %in% c("DK011", "DK012", "DK013", "DK014", "DK021", "DK022", "DK031", "DK032", "DK041", "DK042", "DK050", "DKZZZ")) %>%
	 select("Year", "Regio_id", "Per_capita", "Population")
```

**Country level**
 

```{r Mean: GDP Per Capita in Denmark}
	summarise(DK, GDP_per_Capita = mean(Per_capita))
```
This summarise above shows total GDP per capita for the last 14 years. It is 44,208.62, which is higher than the one we found for all the countries combined. Which means that Denmark has a higher GDP per capita than the average for our countries.

```{r}
summary(DK)
```
Denmark has no data from before 2007, so there are less data to be collected. When we look at the summary above, we see that Denmark has had an increase in both GDP per capita and population over the past 14 years.

**Regions in Denmark**

To make it even more specific, we chose to look at a specific year, and find out which regions are most whealty that year and which regions come out poorly that exact year. We choose 2020, which is the last year that is included in the calculation, and therefore closest to 2022, which we are in today. We also chose to look at the 5 richest and the 5 poorest regions to see if there were major differences. We will do the same with all of our five countries. 

```{r the whealtiest regions in Denmark}
GDPDK <- BNP2%>%
  filter(grepl("DK...", Regio_id)) %>%
  filter(Year==2020) %>%
  select(Regio_id, Per_capita)
slice_max(GDPDK, Per_capita, n=5)
```

```{r The poorest regions in Denmark}
slice_min(GDPDK, Per_capita, n=5)
```

Denmark has 11 Nuts 3 regions, so chosing five from each category may be to much, but in the larger countries we will se a bigger difference. 
The five Whealties regions in Denamrk are kobenhagen (DK011), Kobenhagen area (DK012), Sydjylland (DK032), Vestjylland (DK041) and Østjylland (DK042). 
the poorest regions in Denmark are Vest- og Sydjælland (DK022), Bornholm (DK014), Østsjælland (DK021), Fyn (DK031) and NordJylland (DK050)

There are not big difference in the different regions. It is Copenhagen and the surrounding area that stand out the most, but since it is the capital of Denmark, we believe that most rich people live there. 

###France
France is a country in Western Europe, and also has colonies in other parts of the world. Paris is the capital of France. France has the largest land areas in the EU, something we see again in that they have over a hundred nuts in 3 regions. 

```{r France}
#| echo = FALSE
FR <- BNP2 %>%
filter(Regio_id %in% c("FR101", "FR102", "FR103", "FR104", "FR105", "FR106", "FR107", "FR108", "FRB01", "FRB02", "FRB03", "FRB04", "FRB05", "FRB06" , "FRC11", "FRC12","FRC13", "FRC14", "FRC21", "FRC22, FRC23", "FRC24", "FRD11", "FRD12","FRD13", "FRD21", "FRD22, FRE11", "FRE12", "FRE21", "FRE22", "FRE23","FRF11", "FRF12", "FRF21", "FRF22, FRF23", "FRF24", "FRF31", "FRF32", "FRF33","FRF34", "FRG01", "FRG02", "FRG03, FRG04", "FRG05", "FRH01", "FRH02", "FRF03, FRH04", "FRI11", "FRI12", "FRI13", "FRI14, FRI15", "FRI21", "FRI22", "FRI23, FRI31", "FRI32", "FRI33", "FRI34","FRJ11", "FRJ12",	"FRJ13",	"FRJ14",	"FRJ15",	"FRJ21",	"FRJ22",	"FRJ23",	"FRJ24",	"FRJ25",	"FRJ26",	"FRJ27"	,"FRJ28",	"FRK11",	"FRK12",	"FRK13",	"FRK14",	"FRK21",	"FRK22",	"FRK23",	"FRK24",	"FRK25",	"FRK26",	"FRK27",	"FRK28",	"FRL01",	"FRL02",	"FRL03",	"FRL04",	"FRL05",	"FRL06",	"FRM01",	"FRM02","FRXXX",	"FRY10",	"FRY20",	"FRY30",	"FRY40",	"FRY50")) %>%
 select("Year", "Regio_id", "Per_capita", "Population")
```

```{r}
summary(FR)
```

In the summary of France there was a hug differense in min and max. this is because France has colonies in other countries that are in cluded. These colonies are located in Africa and South America which have a negative effect on the overall GDP of France. For further research we have chosen to remove these regions from the data set.

```{r France without the FRY regions}
#| echo = FALSE
FR1 <- BNP2 %>%
filter(Regio_id %in% c("FR101", "FR102", "FR103", "FR104", "FR105", "FR106", "FR107", "FR108", "FRB01", "FRB02", "FRB03", "FRB04", "FRB05", "FRB06" , "FRC11", "FRC12","FRC13", "FRC14", "FRC21", "FRC22, FRC23", "FRC24", "FRD11", "FRD12","FRD13", "FRD21", "FRD22, FRE11", "FRE12", "FRE21", "FRE22", "FRE23","FRF11", "FRF12", "FRF21", "FRF22, FRF23", "FRF24", "FRF31", "FRF32", "FRF33","FRF34", "FRG01", "FRG02", "FRG03, FRG04", "FRG05", "FRH01", "FRH02", "FRF03, FRH04", "FRI11", "FRI12", "FRI13", "FRI14, FRI15", "FRI21", "FRI22", "FRI23, FRI31", "FRI32", "FRI33", "FRI34","FRJ11", "FRJ12",	"FRJ13",	"FRJ14",	"FRJ15",	"FRJ21",	"FRJ22",	"FRJ23",	"FRJ24",	"FRJ25",	"FRJ26",	"FRJ27"	,"FRJ28",	"FRK11",	"FRK12",	"FRK13",	"FRK14",	"FRK21",	"FRK22",	"FRK23",	"FRK24",	"FRK25",	"FRK26",	"FRK27",	"FRK28",	"FRL01",	"FRL02",	"FRL03",	"FRL04",	"FRL05",	"FRL06",	"FRM01",	"FRM02","FRXXX")) %>%
 select("Year", "Regio_id", "Per_capita", "Population")
```

**Country level**
```{r Mean GDP Per Capita in France}
	summarise(FR1, GDP_per_Capita = mean(Per_capita))
```
Now we have removed the colony regions. This summarise above shows total GDP per capita for the last 18 years. It is 27 289,7 which is lower than the one we found for all the countries combined. Which means that france has a lower GDP per capita than the average for our countries.  

```{r}
summary(FR1)
```	

In the summary above, we see that France has had an big increase in both GDP per capita and population over the past 18 years. We see a fairly large increase from the 3rd quartile to max. Something we will look at more closely when we look at the richest and poorest regions. 

**Regions in France**

```{r The whealtiest regions in France}
GDPFR <- FR1%>%
  filter(grepl("FR...", Regio_id)) %>%
  filter(Year==2020) %>%
  select(Regio_id, Per_capita)
slice_max(GDPFR, Per_capita, n=5)
```

```{r The poorest regions in France}
slice_min(GDPFR, Per_capita, n=5)
```

The five wheltiest regions are Paris (FR101), Hauts-de-seine (FR105), Rhône (FRK26), Essonne(FR104), Haute-Garonne(FRJ23). Paris og Hauts-de-seine stands out clarly from the other tree regions with a large GDP pr capita.
The five poorest regions Creuse (FRI22), Ariège (FRj21), Meuse(FRF32), Gers(FRJ24) and Aisne (FRE21) these regions have quite the same GDP pr capita. 

###Hungary
Hungary is a country in central Europe, the country's capital is Budapest.

```{r Hungary}
#| echo = FALSE
HU <- BNP2 %>%
filter(Regio_id %in% c("HU110", "HU120","HU211","HU212", "HU213", "HU221", "HU222","HU223","HU231", "HU232", "HU233", "HU311", "HU312", "HU313", "HU321", "HU322", "HU323", "HU331", "HU332", "HU333", "HUXXX")) %>%
 select("Year", "Regio_id", "Per_capita", "Population")
	
```

**Country level**

```{r Mean: GDP Per Capita in Hungary}
	summarise(HU, GDP_per_Capita = mean(Per_capita))
```
This summarise above shows total GDP per capita for the last 18 years. It is 8 781,69 which is very low than the one we found for all the countries combined. Which means that Hungary has a low GDP per capita than the average for our countries.

```{r}
summary(HU)
```
In the summary above, we see that Hungary has had an increase in both GDP per capita and population over the past years. We see a fairly large increase from the 3rd quartile to max. Something we will look at more closely when we look at the richest and poorest regions.

**Regions in Hungary**

```{r The whealtiest regions in Hungary}
GDPHU <- BNP2%>%
  filter(grepl("HU...", Regio_id)) %>%
  filter(Year==2020) %>%
  select(Regio_id, Per_capita)
slice_max(GDPHU, Per_capita, n=5)
```

```{r The poorest regions in Hungary}
slice_min(GDPHU, Per_capita, n=5)
```

Hungary has 20 regions. the five Whelties is Budapest (HU110), Gyôr-Moson.Sopron (hu221), Fejèr (HU211), Komàrom-Esztergom (hu211) and Vas (HU222). Budapest is the richest region, while the other four are more even. The poorest regions are Nògràd(HU313), Szabolcs-Szatmàr-Bereg(HU323), Bèkès(HU332), Somogy (HU232) and Jàsz-Nagykun-Szolnok(HU322). Nògràd have very low GDP pr capita. and stands out compared to the others.  

### Portugal
Portugal is a country in southern Europe. Lisbon is the capital. Portugal also has two archipelagos, each representing a different region.

```{r Portugal}
#| echo = FALSE
#Gen data Portugal
PT <- BNP2 %>%
filter(Regio_id %in% c("PT111","PT112","PT119","PT11A","PT11B","PT11C", "PT11D","PT11E",	"PT16B",	"PT16D",	"PT16E",	"PT16F",	"PT16G",	"PT16H",	"PT16I",	"PT16J",	"PT170",	"PT181",	"PT184",	"PT185",	"PT186",	"PT187",	"PT200",	"PT300")) %>%
 select("Year", "Regio_id", "Per_capita", "Population") 

```
**Country level**
```{r Mean: GDP Per Capita in Portugal}
	summarise(PT, GDP_per_Capita = mean(Per_capita))
```
This summarise above shows total GDP per capita for the last 20 years. It is 14 415,77 which is lower than the one we found for all the countries combined. Which means that Portugal has a low GDP per capita than the average for our countries.

```{r}
summary(PT)
```
In the summary above, we see that Portugal has had an increase in both GDP per capita and population over the past years. Population has had a big increase, and we see a huge difference from 3rd quartile until max in population.  

**Regions in Portugal**

```{r The whealtiest regions in Portugal}
GDPPT <- BNP2%>%
  filter(grepl("PT...", Regio_id)) %>%
  filter(Year==2020) %>%
  select(Regio_id, Per_capita)
slice_max(GDPPT, Per_capita, n=5)
```

```{r The poorest regions in Portugal}
slice_min(GDPPT, Per_capita, n=5)
```

Portugal has 25 regions. The wheltiest are Lisboa(PT170), Alentejo Litoral (PT181), Algarve (PT150), Região de Leiria (PT16F) and Região de Aveiro (PT16D). We can se that Lisboa has a litle higher GDP pr capita then the rest of the wheltiest regions. The poorest regions are Tãmega e Sousa (PT11C), Alto Tãmega (PT11B), Beiras e Serra da Estrela (PT16J), Douro (PT11D) and Alto Alentejo (PT186). There are not large differences between the richest and poorest regions.     

###Slovakia

Slovakia is a country in central Europe. It is similar to Denmark, a country that does not have so many NUTS3 regions. We therefore have to keep an eye on any outcomes. The capital in Slovakia is Bratislava. 

```{r Slovakia}
#| echo = FALSE
SK <- BNP2 %>%
filter(Regio_id %in% c("SK010", "SK021","SK022","SK023", "SK031", "SK032", "SK041", "SK042")) %>%
 select("Year", "Regio_id", "Per_capita", "Population")
```
**Country level**
```{r Mean: GDP Per Capita in Slovakia}
	summarise(SK, GDP_per_Capita = mean(Per_capita))
```
This summarise above shows total GDP per capita for the last 20 years. It is 12 493,33 which is lower than the one we found for all the countries combined. Which means that Slovakia has a lower GDP per capita than the average for our countries.

```{r}
summary(SK)
```
In the summary above, we see that Slovakia has had an increase in both GDP per capita and population over the past years. GDP pr capita has had a big increase, and we see a difference from 3rd quartile until max in population. In poplutaion we can se a Steady development.  

**Regions in Slovakia**
```{r The whealtiest regions in Slovakia}
GDPSK <- BNP2%>%
  filter(grepl("SK...", Regio_id)) %>%
  filter(Year==2020) %>%
  select(Regio_id, Per_capita)
slice_max(GDPSK, Per_capita, n=3)
```

```{r The poorest regions in Slovakia}
slice_min(GDPSK, Per_capita, n=3)
```

Slovakia has 8 regions. Therefore we have only looked at 3 regions in each category. The three Whealtiest. Bratislava (SK010), Trnava (SK021) and Zilina (SK031). again we see that the capital has a significantly higher GDP per capita than the other regions. the poorest regions are Presov (SK041), Banska Bystrica (SK032) and Kosice (SK042). the lowest is slightly lower than the other.  

## Descriptive Statistics regional inequity (Gini Nuts2) and discuss briefly if there are noteworthy outliers

Furthermore, we will use the data to calculate population waterproof GDP Ginie coefficients for our countries at a NUTS2 () level. 

A Gini coefficient must be between 0 and 1. If it's 0, it means that there is little inequality, and if it's closer to 1, it means that there is a greater degree of inequality between rich and poor. We calculate a Gini coefficient by looking at how much wealth and income there is in a country and then how it is distributed among the population.
when we have calculated the gini coefficients, we will also run a test on the data we have to see if we find outliers. Outliers are values that are either very high or very low compared to the other data we have.

First out is Denmark. 

### Denmark 

```{r Denmark gini}
#| echo = FALSE
#Nuts 2 id
DK %<>%  
  mutate(id_nuts2 = substr(Regio_id,1,4)) 
#Nuts 1 id
DK %<>%  
  mutate(id_nuts0 = substr(Regio_id,1,2))

#gen weighted gini
#for all
gini.wtd(DK$Per_capita, w = DK$Population)


DK %<>% 
   group_by(id_nuts2, Year) %>%
  mutate(gini_n6 = gini.wtd(Per_capita, w = Population)) %>%
  ungroup() # to remove grouping

summary(DK$gini_n6 )

```

```{r NUTS2 in Denmark}
  ggplot(DK, aes(x = Year, y=gini_n6, fill=id_nuts2, color=id_nuts2)) +
  geom_point(lwd = .8) +
   labs(x = "Year", y = "GDP")
```

```{r Outliers in Denmark}
DKoutliers <- DK %>%
  filter(gini_n6==0) %>%
  distinct(id_nuts2)
DKoutliers
```

In Denmark, we can see that the Gini coefficient is 0.15, which shows us that there is not a big difference between whealty and poor. We can also see that Denmark has a region (DK05) which is an outlier. In this region, no data has been recorded over 0 for the last 20 years. As we also have seen is that Denmark is a small country with few NUTS2 regions Which doesn't givs us much data to work with.
The Outliers region is Nordjylland, which only has one single province.

### France
```{r France gini}
#| echo = FALSE
#Nuts 2 id
FR1 %<>%  
  mutate(id_nuts2 = substr(Regio_id,1,4)) 
#Nuts 1 id
FR1 %<>%  
  mutate(id_nuts0 = substr(Regio_id,1,2))

#gen weighted gini
#for all
  gini.wtd(FR1$Per_capita, w = FR1$Population)


FR1 %<>% 
   group_by(id_nuts2, Year) %>%
  mutate(gini_n3 = gini.wtd(Per_capita, w = Population)) %>%
  ungroup() # to remove grouping

summary(FR1$gini_n3 )

```

```{r NUTS2 regions in France}
  ggplot(FR1, aes(x = Year, y=gini_n3, fill=id_nuts2, color=id_nuts2)) +
  geom_point(lwd = .8) +
   labs(x = "Year", y = "GDP")
```
```{r}
FRoutliers <- FR1 %>%
  filter(gini_n3==0) %>%
  distinct(id_nuts2)
FRoutliers
```

In France, we can see that the Gini coefficient is 0.21, which shows us that France has a slightly higher gini than Denmark had, which means that the inequality is slightly greater in France. We can also see that France has two regions which are outliers Upper Normandy (FRD2) and Nord-Pas-de-Calais (FRE1).  


### Hungary
```{r Hungary gini}
#| echo = FALSE
#Nuts 2 id
HU %<>%  
  mutate(id_nuts2 = substr(Regio_id,1,4)) 
#Nuts 1 id
HU %<>%  
  mutate(id_nuts0 = substr(Regio_id,1,2))

#gen weighted gini
#for all
gini.wtd(HU$Per_capita, w = HU$Population)


HU %<>% 
   group_by(id_nuts2, Year) %>%
  mutate(gini_n4 = gini.wtd(Per_capita, w = Population)) %>%
  ungroup() # to remove grouping

summary(HU$gini_n4 )

```

```{r NUTS2 regions in Hungary}
  ggplot(HU, aes(x = Year, y=gini_n4, fill=id_nuts2, color=id_nuts2)) +
  geom_point(lwd = .8) +
   labs(x = "Year", y = "GDP")
```

```{r}
HUoutliers <- HU %>%
  filter(gini_n4==0) %>%
  distinct(id_nuts2)
HUoutliers
```
In Hungary , we can see that the Gini coefficient is 0.28, which shows us that Hungary has a higher gini than both denmark and France had, which means that the inequality is slightly greater in Hungary. We can also see that Hungary has two regions which are outliers Budabest (HU11) and Pest (HU12). Pest and Budapest hasn't had any data for the periode that we are looking in.   

### Portugal

```{r Portugal gini}
#| echo = FALSE
#Nuts 2 id
PT %<>%  
  mutate(id_nuts2 = substr(Regio_id,1,4)) 
#Nuts 1 id
PT %<>%  
  mutate(id_nuts0 = substr(Regio_id,1,2))

#gen weighted gini
#for all
gini.wtd(PT$Per_capita, w = PT$Population)


PT %<>% 
   group_by(id_nuts2, Year) %>%
  mutate(gini_n2 = gini.wtd(Per_capita, w = Population)) %>%
  ungroup() # to remove grouping

summary(PT$gini_n2 )

```

```{r}
  ggplot(PT, aes(x = Year, y=gini_n2, fill=id_nuts2, color=id_nuts2)) +
  geom_point(lwd = .8) +
   labs(x = "Year", y = "GDP")
```

```{r}
PToutliers <- PT %>%
  filter(gini_n2==0) %>%
  distinct(id_nuts2)
PToutliers
```
In Portugal, we can see that the Gini coefficient is 0.16, which shows us that there is not a big difference between whealty and poor. We can also see that Portugal has tree regions Lisboa(PT17), Regiäo Autònoma dos Acores (PT20) and Regiäo Autònoma da Madeira (PT30) which are outliers. Regiäo Autònoma dos Acores and Regiäo Autònoma da Madeira are both archipelagos belonging to Portugal which may be the reason why they are outliers.  In all these tre regions, no data has been recorded for the last 20 years. Portugal doesn't have many NUTS 2 regions, and when three of them have no value, there is not much confidence in the result we get.

### Slovakia
```{r Slovakia gini}
#| echo = FALSE
SK %<>%
  mutate(id_nuts2 = substr(Regio_id,1,4))

SK %<>%
  mutate(id_nuts0 = substr(Regio_id,1,2))

gini.wtd(SK$Per_capita, w = SK$Population)

SK %<>%
  group_by(id_nuts2, Year) %>%
  mutate(gini_n5 = gini.wtd(Per_capita, w = Population)) %>%
ungroup()

summary(SK$gini_n5)

```

```{r}
  ggplot(SK, aes(x = Year, y=gini_n5, fill=id_nuts2, color=id_nuts2)) +
  geom_point(lwd = .8) +
   labs(x = "Year", y = "GDP")
```

```{r}
SKoutliers <- SK %>%
  filter(gini_n5==0) %>%
  distinct(id_nuts2)
SKoutliers
```
In Slovakia, we can see that the Gini coefficient is 0.30, which is the highest Gini we have found for our countries. Slovakia has on region that is an outliers which are (SK01). That leavs only Slovakia with three regions from which we obtain data. which is not a lot of data.

To summarize what has been done in assignment 1, we have calculated GDP per capita for all the countries combined and per country we have been given. We saw that when we collected all the countries we got 22,805.13 Euros in GDP per capita. Denmark had a significantly higher GDP per capita than the other countries. Hungary had the lowest with only 8781.69. France has colonies in other continents, we chose to remove these regions, this so that GDP would not be affected by these regions that belong to others continents.
Then we calculated the Gini coefficient for all the nuts 2 regions in our countries. Again we saw that Denmark came out best with a Gini of 0.15. Slovakia had the highest Gini at 0.30. Portugal which only had 6 NUTS 2 regions were 3 of these outliers, they got a pretty good Gini of 0.16. but we doubt whether this is a valid result, since we had so limited regions that had data. All countries had regions that were outliers. In some of the countries there were small regions, while in other countries it was the capitals that were the outliers.

# Assignment 2 
At the second assigment we are looking at growth and inequity. We are going to estimate the effete if regional development on regional inequality, for the year 2010. Then we will disuse the goodness of fit of our estimated model.
We will plot the relationship between regional development and regional inequality and the fitted line corresponding to our estimate. We are also going to plot the residuals against the predicted values of our model.
There will be a discussion about the classical assumptions OLS in light of our data and plots and other determinants of inequity.
We will also go back on Eurostat´s webpages and  download EurostatLinks to an external site. It will be for our subset of countries regional (NUTS2, j) data related to transport infrastructure, education and demographics. We are suppose to select on variable per category that we would like to explore further in there relationship to regional inequality.
We will try to estimate a multiple linear regression model with our new variables for 2010 and give a small interpretation of our findings.
In the end we will discuss the overall fit of our model and the inference related to our findings.

### Data set: 

We want to look at the amount of people who have higher education in the education data set and how many railways lines there is in kilometers when we look in the transport dataset. In the demographic data set we want to see the life expectancy age is in age.

```{r Data set Education }
#| echo = FALSE
Education <- read_csv('edat_lfse_04__linear 2.csv') %>%
  select(unit,isced11,geo,age,TIME_PERIOD,OBS_VALUE) %>%
  filter(unit=="PC" & isced11=="ED0-2" & age=="Y25-64" & (grepl('DK..', geo) | grepl('FR..', geo) | grepl('HU..', geo)| grepl('PT..', geo) | grepl('SK..', geo))) %>%
  mutate(Edu = OBS_VALUE, Year2=TIME_PERIOD, Region2=geo) %>%
  select(Region2, Year2, Edu)
```

```{r Data set Railways}
#| echo = FALSE
Transport <- read_csv('tran_r_net_1_Data.csv') %>%
  select(UNIT,TIME,GEO,Value,TRA_INFR) %>%
  filter(UNIT=="Kilometre" & TRA_INFR== "RL" & (grepl('DK..', GEO) | grepl('FR..', GEO) | grepl('HU..', GEO)| grepl('PT..', GEO) | grepl('SK..', GEO))) %>%
  mutate(Railway = Value, Year2 = TIME, Region2=GEO) %>%
  select(Region2, Year2, Railway)
```

```{r Data set life expectancy age }
#| echo = FALSE
Lifeexp <- read_csv('demo_r_mlifexp_1_Data.csv') %>%
select(TIME,GEO,SEX,AGE,UNIT,Value) %>%
filter(UNIT=="YEAR" & SEX == "Total" & (grepl('DK..', GEO) | grepl('FR..', GEO) | grepl('HU..', GEO) | grepl('PT..', GEO) | grepl('SK..', GEO))) %>%
   mutate(lea = Value, Year2 = TIME, Region2=GEO) %>%
  select(Region2,Year2, lea)

```

```{r}
DK %>%
  filter(Year==2010) %>%
ggplot(aes(x =id_nuts2, y=gini_n6, fill=id_nuts2, color=id_nuts2)) +
  geom_point(lwd = .8) +
   labs(x = "id_nuts2", y = "Gini_n6")
```

```{r
DK2<- DK %>%
  left_join(Education, by = c("Year"))
DK2<- DK2 %>%
  mutate(nuts0 = substr(Region2,1,2))
DK2 %>%
  filter(Year==2010 & nuts0=="DK") %>%
ggplot(aes(x =Edu, y=gini_n6, fill=id_nuts2, color=id_nuts2)) +
  geom_point(lwd = .8) +
   labs(x = "Education", y = "Gini")
```

```{r}
FR1 %>%
  filter(Year==2010) %>%
ggplot(aes(x =id_nuts2, y=gini_n3, fill=id_nuts2, color=id_nuts2)) +
  geom_point(lwd = .8) +
   labs(x = "id_nuts2", y = "Gini_n3")
```

```{r
FR2<- FR1 %>%
  left_join(Education, by = c("Year2"))
FR2<- FR2 %>%
  mutate(nuts0 = substr(Region2,1,2))
FR2 %>%
  filter(Year==2010 & nuts0=="FR") %>%
ggplot(aes(x =Edu, y=gini_n3, fill=id_nuts2, color=id_nuts2)) +
  geom_point(lwd = .8) +
   labs(x = "Education", y = "Gini")
```

```{r}
SK %>%
  filter(Year==2010) %>%
ggplot(aes(x =id_nuts2, y=gini_n5, fill=id_nuts2, color=id_nuts2)) +
  geom_point(lwd = .8) +
   labs(x = "id_nuts2", y = "Gini_n5")
```

```{r
SK2<- SK %>%
  left_join(Education, by = c("Year5"))
SK2<- SK2 %>%
  mutate(nuts0 = substr(Region2,1,2))
SK2 %>%
  filter(Year==2010 & nuts0=="SK") %>%
ggplot(aes(x =Edu, y=gini_n5, fill=id_nuts2, color=id_nuts2)) +
  geom_point(lwd = .8) +
   labs(x = "Education", y = "Gini")
```

```{r}
DK2010 <- DK %>%
    filter(Year==2010 & id_nuts0=="DK") 
FR2010 <- FR1 %>%
    filter(Year==2010 & id_nuts0=="FR") 
HU2010 <- HU %>%
    filter(Year==2010 & id_nuts0=="HU") 
PT2010 <- PT %>%
    filter(Year==2010 & id_nuts0=="PT") 
SK2010 <- SK %>%
    filter(Year==2010 & id_nuts0=="SK") 


#Estimates 
lm.1 = lm(Region2 ~ edu , data = Education) 
lm.2 = lm(Region2 ~ Railway, data = Education)
lm.3 = lm(Region2 ~ edu + Railway, Education)
#Gen Table
  huxreg(
  list("Model 1" = lm.1, "Model 2" = lm.2, "Model 3" = lm.3),
  statistics = c(N = "nobs", R2 = "r.squared"),
  coefs = c(Education = "edu","Railway", const. = "(Intercept)"),
  note = "Note: {stars} T statistics in brackets."
  )
  
#estimates 
lm.4 = lm(Region2 ~ edu , data = Education) 
lm.5 = lm(Region2 ~  lea, data = Education)
lm.6 = lm(Region2 ~ edu + lea, data = Education)
#Gen Table
  huxreg(
  list("Model 1" = lm.4, "Model 2" = lm.5, "Model 3" = lm.6),
  statistics = c(N = "nobs", R2 = "r.squared"),
  coefs = c(Education = "edu","lea", const. = "(Intercept)"),
  note = "Note: {stars} T statistics in brackets."
  )
}
```


Slovakia 



