---
title: "Econometriscs assignment"
author: "Heidi Marie Rolfsnes and Ann Elisabeth Jacobsen"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r Packages}
suppressMessages(library(tidyverse))
suppressMessages(library(lubridate))
suppressMessages(library(tibble))
suppressMessages(library(readr))
suppressMessages(library(knitr))
suppressMessages(library(dplyr))
options(scipen = 999)
```

This is a collection of assignments in the subject econometrics MSB104.

In this assignment we are looking at five European countries. Denmark, France, Hungary, Portugal and Slovakia. 
In the first assignment we have collected data from Eurostats, the data contains GDP and populations for the countries but also at NUTS3 level for the last 20 years. 

We collected 2 datasets, and the first thing we did was to clean the list and remove data that didn’t have any valuables. We changed the names on some of the variables. 
After that we merged the two datasets into one.


```{r GDP from Portugal, France, Hungary, Slovakia and Denmark}
BNP<- read.csv("nama_10r_3gdp.csv")
BNP <- BNP %>% 
  select(unit, geo, TIME_PERIOD, OBS_VALUE) %>%
      rename(GDP = "OBS_VALUE",Year = "TIME_PERIOD", Land = "geo") 
```

```{r  Population from Portugal, France, Hungary, Slovakia and Denmark}
Pop<- read_csv("demo_r_pjanaggr3.csv", show_col_types = FALSE)
Pop <- Pop %>% 
  select(geo, TIME_PERIOD, OBS_VALUE) %>%
      rename(Population = "OBS_VALUE",Year_pop = "TIME_PERIOD") 
 
  
```

```{r GNP and Population - together}
 BNP2<- BNP %>%
      select(unit, Land,Year, GDP) %>%
      left_join(Pop, by = c("Year" = "Year_pop", "Land" = "geo"))
     
```

Then we calculated the GDP pr capita. And this we did by dividing the GDP on the population. 

```{r Calculate GDP per capita}
BNP2 <- BNP2 %>%
mutate(Per_capita =   GDP/Population*1000000) %>%
na.omit()
#NA variables are removed
```



```{r Denmark}
DK <- group_by(BNP2, Land, Year) %>%
filter(Land =="DK")
	summarise(DK, GDP_per_Capita = mean(Per_capita))
```

```{r}
Summary(DK)
```

```{r France}
FR <- group_by(BNP2, Land, Year) %>%
filter(Land == "FR")
	summarise(FR, GDP_per_Capita = mean(Per_capita))
```
```{r}
Summary(FR)
```

```{r Hungary}
HU <- group_by(BNP2, Land, Year) %>%
filter(Land == "HU")
	summarise(HU, GDP_per_Capita = mean(Per_capita))
```
```{r}
Summary(HU)
```

```{r Slovakia}
SK <- group_by(BNP2, Land, Year) %>%
filter(Land == "SK")
	summarise(SK, GDP_per_Capita = mean(Per_capita))
```
```{r}
Summary(SK)
```

```{r Portugal}
PT <- group_by(BNP2, Land, Year, Population, GDP) %>%
filter(Land == "PT")
	summarise(PT, GDP_per_Capita = mean(Per_capita))
```

```{r - Portugal samendrag}
summary(PT)
```




